\documentclass[12pt]{article}
\usepackage[left=1in, right=1in,top=1.25in,bottom=1in]{geometry}

%\usepackage{newpxtext,newpxmath}
%\usepackage{amsfonts}
\usepackage{tgtermes}
\usepackage{color}
\usepackage{bold-extra}
\usepackage{setspace}
%\pagenumbering{gobble}
\usepackage{setspace}
\setstretch{1.1}
%\onehalfspacing

%\fontsize{12pt}{15pt}\selectfont

\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{Huan Q. Bui}
\rhead{Application for UC Berkeley Physics}
%\cfoot{center of the footer!}
%\renewcommand{\headrulewidth}{0.4pt}
%\renewcommand{\footrulewidth}{0.4pt}

\begin{document}
\begin{center}
	\textbf{Statement of Purpose}
\end{center}
I am captivated by the interplay between theory and experiment in quantum information science, condensed matter, and atomic, molecular, and optical physics. In particular, I am interested in  quantum simulations as well as experiments with ultracold gases for quantum science and fundamental physics. In May 2021, I will complete my undergraduate studies at Colby College with two Honors Theses on experimental atomic physics and mathematical analysis. My next objective is to expand and subsequently apply my research training to address an important open problem in quantum science. To that end, the Physics Ph.D. program at UC Berkeley is a fantastic option.  \\ 
	
\input{content}
	
At Berkeley, I would like to focus my efforts on quantum science and expanding my teaching capacity. I have contacted Professor Ehud Altman, whose research on the dynamics of quantum circuits aligns directly with my current interests. Based on our exchange, he feels that Berkeley Physics will be a good fit for me and encourages to me apply. I also contacted Professor Daniel Stamper-Kurn and am interested in his experiments with optical kagome lattice and cold atomic mixtures. Finally, I am attracted to Professor Norman Yao's research on many-body localization and thermalization. Upon receiving my Ph.D., I aim to continue research in quantum science and eventually teach at a research-oriented university. Ultimately, I would like to make impactful contributions to the continually growing body of work in this field. I believe that admission to the Physics Ph.D. program at Berkeley is an ideal step towards this goal. \\
	
	
\noindent Thank you for your consideration. \\
	
\noindent \today














	
	
	
	
	
\end{document}