\documentclass[12pt]{article}
\usepackage[left=1in, right=1in,top=1.25in,bottom=1in]{geometry}

%\usepackage{newpxtext,newpxmath}
%\usepackage{amsfonts}
\usepackage{tgtermes}
\usepackage{color}
\usepackage{bold-extra}
\usepackage{setspace}
%\pagenumbering{gobble}
\usepackage{setspace}
\setstretch{1.1}
%\onehalfspacing

%\fontsize{12pt}{15pt}\selectfont

\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{Huan Q. Bui}
\rhead{Application for Yale Physics}
%\cfoot{center of the footer!}
%\renewcommand{\headrulewidth}{0.4pt}
%\renewcommand{\footrulewidth}{0.4pt}

\begin{document}
\begin{center}
	\textbf{Statement of Purpose}
\end{center}
I am captivated by the interplay between theory and experiment in quantum information science, condensed matter, and atomic, molecular, and optical physics. In particular, I am interested in  quantum simulations as well as experiments with ultracold gases for quantum science and fundamental physics. In May 2021, I will complete my undergraduate studies at Colby College with two Honors Theses on experimental atomic physics and mathematical analysis. My next objective is to expand and subsequently apply my research training to address an important open problem in quantum science. To that end, the Physics Ph.D. program at Yale is a fantastic option.  \\ 

\input{content}

At Yale, I would like to focus my efforts on quantum science and expanding my teaching capacity. I have corresponded with Professor Steven Girvin, whose research on quantum information theory directly aligns with my current interests. I am also interested in Professor Robert Schoelkopf's work on superconducting devices for quantum computing and Professor Glazman's theoretical research on low-dimensional quantum systems. Upon receiving my Ph.D., I aim to continue research in quantum science and eventually teach at a research-oriented university. Ultimately, I would like to make impactful contributions to the continually growing body of work in this field. I believe that admission to the Physics Ph.D. program at Yale is an ideal step towards this goal. \\

\noindent Thank you for your consideration. \\

\noindent \today


	
	
	
\end{document}