\documentclass{article}
\usepackage{physics}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{framed}
\usepackage{authblk}
\usepackage{empheq}
\usepackage{amsfonts}
\usepackage{esint}
\usepackage[makeroom]{cancel}
\usepackage{dsfont}
\usepackage{centernot}
\usepackage{mathtools}
\usepackage{subcaption}
\usepackage{bigints}
\usepackage{amsthm}
\theoremstyle{definition}
\newtheorem{lemma}{Lemma}
\newtheorem{defn}{Definition}[section]
\newtheorem{prop}{Proposition}[section]
\newtheorem{rmk}{Remark}[section]
\newtheorem{thm}{Theorem}[section]
\newtheorem{exmp}{Example}[section]
\newtheorem{prob}{Problem}[section]
\newtheorem{sln}{Solution}[section]
\newtheorem*{prob*}{Problem}
\newtheorem{exer}{Exercise}[section]
\newtheorem*{exer*}{Exercise}
\newtheorem*{sln*}{Solution}
\usepackage{empheq}
\usepackage{tensor}
\usepackage{xcolor}
%\definecolor{colby}{rgb}{0.0, 0.0, 0.5}
\definecolor{MIT}{RGB}{163, 31, 52}
\usepackage[pdftex]{hyperref}
%\hypersetup{colorlinks,urlcolor=colby}
\hypersetup{colorlinks,linkcolor={MIT},citecolor={MIT},urlcolor={MIT}}  
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}

\usepackage{newpxtext,newpxmath}
\newcommand*\widefbox[1]{\fbox{\hspace{2em}#1\hspace{2em}}}

\newcommand{\p}{\partial}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\lag}{\mathcal{L}}
\newcommand{\nn}{\nonumber}
\newcommand{\ham}{\mathcal{H}}
\newcommand{\M}{\mathcal{M}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\K}{\mathcal{K}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\w}{\omega}
\newcommand{\lam}{\lambda}
\newcommand{\al}{\alpha}
\newcommand{\be}{\beta}
\newcommand{\x}{\xi}

\newcommand{\G}{\mathcal{G}}

\newcommand{\f}[2]{\frac{#1}{#2}}

\newcommand{\ift}{\infty}

\newcommand{\lp}{\left(}
\newcommand{\rp}{\right)}

\newcommand{\lb}{\left[}
\newcommand{\rb}{\right]}

\newcommand{\lc}{\left\{}
\newcommand{\rc}{\right\}}


\newcommand{\V}{\mathbf{V}}
\newcommand{\U}{\mathcal{U}}
\newcommand{\Id}{\mathcal{I}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\Z}{\mathcal{Z}}

%\setcounter{chapter}{-1}


\usepackage{enumitem}



\usepackage{listings}
\captionsetup[lstlisting]{margin=0cm,format=hang,font=small,format=plain,labelfont={bf,up},textfont={it}}
\renewcommand*{\lstlistingname}{Code \textcolor{violet}{\textsl{Mathematica}}}
\definecolor{gris245}{RGB}{245,245,245}
\definecolor{olive}{RGB}{50,140,50}
\definecolor{brun}{RGB}{175,100,80}

%\hypersetup{colorlinks,urlcolor=colby}
\lstset{
	tabsize=4,
	frame=single,
	language=mathematica,
	basicstyle=\scriptsize\ttfamily,
	keywordstyle=\color{black},
	backgroundcolor=\color{gris245},
	commentstyle=\color{gray},
	showstringspaces=false,
	emph={
		r1,
		r2,
		epsilon,epsilon_,
		Newton,Newton_
	},emphstyle={\color{olive}},
	emph={[2]
		L,
		CouleurCourbe,
		PotentielEffectif,
		IdCourbe,
		Courbe
	},emphstyle={[2]\color{blue}},
	emph={[3]r,r_,n,n_},emphstyle={[3]\color{magenta}}
}






\begin{document}
\begin{framed}
\noindent Name: \textbf{Huan Q. Bui}\\
Course: \textbf{8.370 - QC}\\
Problem set: \textbf{\#6}\\
Due: Wednesday, Nov 2, 2022\\
Collaborators/References: 
\end{framed}


\noindent \textbf{1. Pauli group, Clifford group} 

\begin{enumerate}[label=(\alph*)]
	\item The Clifford group is 
	\begin{align*}
		\mathcal{C} \equiv \{ \text{unitaries } U : U g U^\dagger \in \mathcal{P}\, \forall g \in \mathcal{P}     \}
	\end{align*}
where $\mathcal{P}$ is the Pauli group. Suppose $A,B\in \mathcal{C}$. Then for any $g\in \mathcal{P}$:
\begin{align*}
	AB g (AB)^\dagger =  A \underbrace{ (BgB^\dagger)}_{\in \mathcal{P}} A^\dagger= A g' A^\dagger \in \mathcal{P}.
\end{align*}
So $AB\in \mathcal{C}$. \textcolor{purple}{How to do the second part here???}
So every element of $\mathcal{C}$ has an inverse. The identity element is simply the identity matrix. Associativity is inherited from associativity of matrix multiplication. So, $\mathcal{C}$ is a group. 
	
	\item The Pauli group for 1 qubit is given by 
	\begin{align*}
		\mathcal{P}_1 = \{ \pm I, \pm iI\,\pm X, \pm iX, \pm Y, \pm i Y, \pm Z, \pm iZ \}.
	\end{align*}
	The Pauli group for $n$ qubits is simply generated, via the tensor product, by the operators in $\mathcal{G}_1$, which are generated by the Pauli matrices $X,Y,Z$. $H$ is unitary. So, it remains to check that $H$ is in $\mathcal{C}_1$. Using the fact that $H^\dagger = H^{-1} = H$, we can simply check that $HXH, HYH, HZH \in \mathcal{P}_2$:
	\begin{align*}
		&HXH = Z \in \mathcal{P}_1 \\
		&HZH = X \in \mathcal{P}_1 \\
		&HYH = -Y \in \mathcal{P}_1
	\end{align*}
	And we're done!
	
	\item To check that the $CNOT$ gate is in $\mathcal{C}$, we check that it is in $\mathcal{C}_2$. $CNOT$ is unitary, so we check that $CNOT \, g \, CNOT^\dagger$ is in $\mathcal{P}_2$ for all generators $g$ of $\mathcal{P}_2$. The generators of $\mathcal{P}_2$ are once again $X,Y,Z$ tensored with the identity matrix either on the first or second qubit. This means there are six cases:
	 \begin{align*}
	 	&CNOT\,X \otimes \Id \,CNOT^\dagger = X\otimes X \in \mathcal{P}_2 \\
	 	&CNOT\,Y \otimes \Id \,CNOT^\dagger = Y\otimes X \in \mathcal{P}_2 \\
	 	&CNOT\,Z \otimes \Id \,CNOT^\dagger = Z\otimes \Id \in \mathcal{P}_2 \\
	 	&CNOT\,\Id \otimes X \,CNOT^\dagger = \Id \otimes X \in \mathcal{P}_2 \\
	 	&CNOT\,\Id \otimes Y \,CNOT^\dagger = Z \otimes Y \in \mathcal{P}_2 \\
	 	&CNOT\,\Id \otimes Z \,CNOT^\dagger = Z \otimes Z \in \mathcal{P}_2 \quad\quad \checkmark
	 \end{align*}
 	Here, the $CNOT$ gate in consideration is one where the first qubit is the control. However, since the other CNOT gate only differs on on which qubits it uses as control and target, we only need to check one of the two CNOTs.
	
	\item We want to check that $T\notin \mathcal{C}_1$. Consider $g = X\in \mathcal{P}_1$. 
	\begin{align*}
		TXT^\dagger = \begin{pmatrix}
			0 & e^{-i\pi4} \\ e^{i\pi/4} & 0
		\end{pmatrix} \notin \mathcal{P}_1.
	\end{align*}
	So $T$ is not in the Clifford group.
\end{enumerate}



\noindent \textbf{2. Gotta erase workbits!}\\




\noindent \textbf{3. Simon's algorithm}

\begin{enumerate}[label=(\alph*)]
	\item Recall Simon's algorithm. After the second application of the Hadamard transform to the first register, the state of the system is 
	\begin{align*}
		\f{1}{2^n} \sum_{k=0}^{2^n-1} \lp \sum_{j=0}^{2^n-1} (-1)^{j\cdot k} \rp \ket{k} \ket{f(j)}.
	\end{align*}
	Now we want to compute the probability of seeing a pair of values $\ket{k} \ket{f(j)}$. This is equal to the square of the amplitude on this state. How many values of $j$ produce $f(j)$? Suppose there are $2L$ different $j$'s for which $f(j)$ gives the same output. Then they must be $\{  j_1, j_2,\dots, j_L, j_1\oplus c, j_2\oplus c, \dots, j_L\oplus c \}$ since $\oplus$ is symmetric. This means that the amplitude for $\ket{k}\ket{f(j)}$ has the form
	\begin{align*}
		\f{1}{2^n} \sum_{i=1}^L \lp (-1)^{j_1\cdot k} + (-1)^{{(j_1\oplus c)}\cdot k }\rp = \f{1}{2^n}(1 + (-1)^{c\cdot k}) \sum_{i=1}^L (-1)^{j_i\cdot k}
	\end{align*}
	This amplitude is nonzero only if $c\cdot k = 0 \mod 2$, so \textbf{YES} the quantum part of Simon's algorithm still always return a binary string with $c\cdot k = 0 \mod 2$. 
	
	\item The probability of measuring a state with $f=1$ is 
	\begin{align*}
		p = \Pr(f=1) = \f{1}{2^{2n}}\sum_{k=0}^{2^n-1} \abs{ (1+(-1)^{c\cdot k})(-1)^{d\cdot k}}^2 = \f{1}{2^{n-1}}\quad \forall c\neq 0.
	\end{align*}

	\textcolor{blue}{I'm not exactly sure how to prove the identity above, but according to my calculation in Mathematica this appears to be the answer. There is probably some clever argument which I haven't had enough time to come up with.}\\

	Let the number of failures $k-1$ before the first success. The probability for this event is 
	\begin{align*}
		\Pr(X=k) = (1-p)^{k-1}p.
	\end{align*}
	The expected value for the random variable $X$, the number of measurements before seeing $f=1$, is 
	\begin{align*}
		E[X] = \sum_{k=0}^\infty k \Pr(X=k) = \f{1}{p}.
	\end{align*}
	So the answer is that we are expected to measure  $\boxed{2^{n-1}}$  times. \\
	
	The amplitude of the pair $\ket{k}\ket{f(j)}$ in the registers is 
	\begin{align*}
		\f{1}{2^n}(1 + (-1)^{c\cdot k}) \sum_{i=1}^L (-1)^{j_i\cdot k}
	\end{align*} 
	Here, $L=1$ for $j=d$ and $L = 2^{n-1}-1$ otherwise. This amplitude is nonzero only if $c\cdot k = 0 \mod 2$. The probability associated with finding a $k$ that is perpendicular to $c$ is thus:
	\begin{align*}
		\f{1}{2^{2n-2}} \abs{\sum_{i=1}^{2^{n-1}-1} (-1)^{j_i\cdot k}}^2 + \f{1}{2^{2n-2}} =  
	\end{align*}
	
	
	So, the probability associated with finding a $k$ that is perpendicular to $c$ is $blah$.   How many vectors will we have to sample to find $n-1$ vectors that are linearly independent? 
	
	

\end{enumerate}



\noindent \textbf{4. Partial transpose}

\begin{enumerate}[label=(\alph*)]
	\item Suppose $M$ is separable, i.e., 
	\begin{align*}
		M = \sum_i \lambda_i \ket{v_i} \bra{v_i} \otimes \ket{w_i}\bra{w_i}
	\end{align*}
	where $\lambda_i$'s are positive. Then the partial transpose of $M$ according to the definition in the problem is
	\begin{align*}
		pt(M) = \sum_i \lambda_i (\ket{v_i}\bra{v_i})^\top \otimes \ket{w_i}\bra{w_i}.
	\end{align*} 
	Since  $\Pi_i = \ket{v_i}\bra{v_i}$ are orthogonal projections, the matrices $(\ket{v_i}\bra{v_i})^\top$ are also orthogonal projections. We may very well consider the transposition as a unitary change of basis in the first qubit and write
	\begin{align*}
		pt(M) = \sum_i \lambda_i \ket{v_i'}\bra{v_i'} \otimes \ket{w_i}\bra{w_i}.
	\end{align*}
	It is clear that the spectrum of $pt(M)$ is exactly the same as that of $M$ in this case, so $pt(M)$ must also be positive. However, we could also be explicit: Let $x = \sum_{i,j} c_{ij} \ket{v_i'}\ket{w_j}$. Then
	\begin{align*}
		\bra{x}  \, pt(M)\, \ket{x} = \sum_i \lambda_i |c_{ii}|^2 \geq 0.
	\end{align*}
	And we're done. 
	
	\item The density matrix for $\ket{\psi} = (1/\sqrt{2})(\ket{00} + \ket{11})$ is 
	\begin{align*}
		\rho = \ket{\psi} \bra{\psi} = \f{1}{2}\begin{pmatrix}
			1 & 0 & 0 & 1 \\
			0 & 0 & 0 & 0 \\
			0 & 0 & 0 & 0 \\
			1 & 0 & 0 & 1
		\end{pmatrix}
	\end{align*}
	From here we find 
	\begin{align*}
		pt(\rho) =  \f{1}{2}\begin{pmatrix}
			1 & 0 & 0 & 0 \\
			0 & 0 & 1 & 0 \\
			0 & 1 & 0 & 0 \\
			0 & 0 & 0 & 1
		\end{pmatrix}.
	\end{align*}
The eigenvalues of this matrix are $-1/2,1/2,1/2,1/2$, so $pt(\rho)$ is not non-negative which implies that $\rho$ is not separable in view of Part (a).
\end{enumerate}


\noindent \textbf{5. Teleporting a qutrit directly}\\

\noindent Instead of embedding the qutrit in a set of qubits of higher dimensions, we can teleport qutrits directly. Let $\omega = e^{2\pi i /3}$, the cube root of unity. Define 
\begin{align*}
	P = \begin{pmatrix}
		1 & 0 & 0 \\ 0 & \omega & 0 \\ 0 & 0 & \omega^2  
	\end{pmatrix} \quad \quad \text{and} \quad\quad 
	T = \begin{pmatrix}
		0 & 1 & 0 \\ 0 & 0 & 1 \\ 1 & 0 & 0
	\end{pmatrix}.
\end{align*}
The analogue of the EPR pair is the state
\begin{align*}
	\ket{EPR_3} = \f{1}{\sqrt{3}}(\ket{00} + \ket{11} + \ket{22})
\end{align*}
and the analogue of the Pauli matrices are the nine matries $P^aT^b$, with $0 \leq a,b< 3$.  We teleport the qutrit as follows:\\

\noindent Alice has some qutrit in state $\ket{\psi} = \al \ket{0} + \be \ket{1} + \gamma \ket{2}$. She now measures her two qutrits (the qutrit in state $\ket{\psi}$ and her half of the $EPR_3$ pair) in the EPR-pair basis which consists of nine states in the form
\begin{align*}
	(\Id \otimes P^a T^b)(\ket{00} + \ket{11} + \ket{22}).
\end{align*}
Alice will then send her measurement result (one of the nine possible ones) to Bob, and Bob will apply one of nine unitaries to his qutrit to obtain $\psi$. In particular, if Alice sees a state associated with $P^a T^b$, then Bob applies $P^a T^b$ to his qutrit. Below we will show explicitly.\\

Here we show the nine-element basis for Alice's measurement, the resulting state on Bob's qutrit, and Bob's corrective unitary for each case:
\begin{align*}
	(1/\sqrt{3})(\Id \otimes P^0 T^0)(\ket{00} + \ket{11} + \ket{22}) &\to \ket{B} = (1/\sqrt{3})\Id(\al\ket{0} + \be\ket{1} + \gamma\ket{2}) \to P^0T^0 \\
	(1/\sqrt{3})(\Id \otimes P^1 T^0)(\ket{00} + \ket{11} + \ket{22}) &\to \ket{B} = (1/\sqrt{3}) P^2(\al\ket{0} + \be\ket{1} + \gamma\ket{2}) \to P^1 T^0\\
	(1/\sqrt{3})(\Id \otimes P^2 T^0)(\ket{00} + \ket{11} + \ket{22}) &\to \ket{B} = (1/\sqrt{3})P^1(\al\ket{0} + \be\ket{1} + \gamma\ket{2}) \to P^2 T^0\\
	(1/\sqrt{3})(\Id \otimes P^0 T^1)(\ket{00} + \ket{11} + \ket{22}) &\to \ket{B} = (1/\sqrt{3})T^2(\al\ket{0} + \be\ket{1} + \gamma\ket{2}) \to P^0 T^1\\
	(1/\sqrt{3})(\Id \otimes P^1 T^1)(\ket{00} + \ket{11} + \ket{22}) &\to \ket{B} = (1/\sqrt{3})P^2  T^2(\al\ket{0} + \be\ket{1} + \gamma\ket{2}) \to P^1T^1\\
	(1/\sqrt{3})(\Id \otimes P^2 T^1)(\ket{00} + \ket{11} + \ket{22}) &\to \ket{B} = (1/\sqrt{3}) P T^2(\al\ket{0} + \be\ket{1} + \gamma\ket{2}) \to P^2 T^1\\
	(1/\sqrt{3})(\Id \otimes P^0 T^2)(\ket{00} + \ket{11} + \ket{22}) &\to \ket{B} = (1/\sqrt{3}) T(\al\ket{0} + \be\ket{1} + \gamma\ket{2}) \to P^0 T^2\\
	(1/\sqrt{3})(\Id \otimes P^1 T^2)(\ket{00} + \ket{11} + \ket{22}) &\to \ket{B} = (1/\sqrt{3}) P^2 T (\al\ket{0} + \be\ket{1} + \gamma\ket{2}) \to P^1 T^2\\
	(1/\sqrt{3})(\Id \otimes P^2 T^2)(\ket{00} + \ket{11} + \ket{22}) &\to \ket{B} = (1/\sqrt{3}) P T(\al\ket{0} + \be\ket{1} + \gamma\ket{2}) \to P^2 T^2.
\end{align*}




\end{document}











