\documentclass[12pt]{article}
\usepackage[left=1in, right=1in,top=1.25in,bottom=1in]{geometry}

%\usepackage{newpxtext,newpxmath}
%\usepackage{amsfonts}
\usepackage{tgtermes}
\usepackage{amsmath}
\usepackage{color}
\usepackage{bold-extra}
\usepackage{setspace}
%\pagenumbering{gobble}
\setstretch{1.1}
%\onehalfspacing


%\fontsize{12pt}{15pt}\selectfont

\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{Huan Q. Bui}
\rhead{Application for Cornell Physics}
%\cfoot{center of the footer!}
%\renewcommand{\headrulewidth}{0.4pt}
%\renewcommand{\footrulewidth}{0.4pt}

\begin{document}
%\noindent Huan Quang Bui \hfill Application for MIT Physics
\begin{center}
	\textbf{Statement of Purpose}
\end{center}
I am captivated by the interplay between theory and experiment in condensed matter and atomic, molecular, and optical physics. In May 2021, I will complete my undergraduate studies at Colby College with two Honors Theses on experimental atomic physics and mathematical analysis. My next objective is to expand and subsequently apply my research training to address a challenging problem in quantum science. To that end, the Physics Ph.D. program at Cornell is a fantastic option.  \\ 


\input{content.tex}


At Cornell, I would like to focus my efforts on quantum science and expanding my teaching capacity. I have contacted Professor Erich Mueller and am attracted to his research on theoretical aspects of ultracold gases, which aligns well with my background in experimental atomic physics and recent interest in theoretical work. In addition, I am drawn to the fact that his research group works closely with experimentalists. I also find Professor Eun-Ah Kim's research on strongly correlated systems very appealing for its use of many fascinating mathematical and numerical methods. Upon receiving my Ph.D., I aim to continue research in quantum science and eventually teach at a research-oriented university. Ultimately, I would like to make impactful contributions to the continually growing body of work in this field. I believe that admission to the Physics Ph.D. program at Cornell is an ideal step towards this goal. \\

\noindent Thank you for your consideration. \\

\noindent \today\\

	











	
	
	
	
	
\end{document}