\documentclass[12pt]{article}
\usepackage[left=1in, right=1in,top=1.25in,bottom=1in]{geometry}

%\usepackage{newpxtext,newpxmath}
%\usepackage{amsfonts}
\usepackage{tgtermes}
\usepackage{amsmath}
\usepackage{color}
\usepackage{bold-extra}
\usepackage{setspace}
%\pagenumbering{gobble}
\usepackage{setspace}
\setstretch{1.1}
%\onehalfspacing

%\fontsize{12pt}{15pt}\selectfont

\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{Huan Q. Bui}
\rhead{Application for CU Boulder Physics}
%\cfoot{center of the footer!}
%\renewcommand{\headrulewidth}{0.4pt}
%\renewcommand{\footrulewidth}{0.4pt}

\begin{document}
\begin{center}
	\textbf{Personal Statement}
\end{center}
I am captivated by the interplay between theory and experiment in quantum information science, condensed matter, and atomic, molecular, and optical physics. In particular, I am interested in  quantum simulations as well as experiments with ultracold gases for quantum science and fundamental physics. In May 2021, I will complete my undergraduate studies at Colby College with two Honors Theses on experimental atomic physics and mathematical analysis. My next objective is to expand and subsequently apply my research training to address an important open problem in quantum science. To that end, the Physics Ph.D. program at CU Boulder is a fantastic option.  \\ 

\input{content} 


At Boulder, I would like to focus my efforts on quantum science and expanding my teaching capacity. I have contacted Professor Jun Ye and am interested in many aspects of his research from precision measurement to ultracold atoms for optical atomic clock. I also find Professor Adam Kaufman's and Professor Graeme Smith's research works very appealing. Upon receiving my Ph.D., I aim to continue research in quantum science and eventually teach at a research-oriented university. Ultimately, I would like to make impactful contributions to the continually growing body of work in this field. I believe that admission to the Physics Ph.D. program at Boulder is an excellent first step towards this goal. \\


\noindent Thank you for your consideration. \\

\noindent \today
	











	
	
	
	
	
\end{document}