\documentclass[12pt]{article}
\usepackage[left=1in, right=1in,top=1.25in,bottom=1in]{geometry}

%\usepackage{newpxtext,newpxmath}
%\usepackage{amsfonts}
\usepackage{tgtermes}
\usepackage{amsmath}
\usepackage{color}
\usepackage{bold-extra}
\usepackage{setspace}
%\pagenumbering{gobble}
\setstretch{1.1}
%\onehalfspacing


%\fontsize{12pt}{15pt}\selectfont

\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{Huan Q. Bui}
\rhead{Application for UIUC Physics}
%\cfoot{center of the footer!}
%\renewcommand{\headrulewidth}{0.4pt}
%\renewcommand{\footrulewidth}{0.4pt}

\begin{document}
%\noindent Huan Quang Bui \hfill Application for MIT Physics
\begin{center}
	\textbf{Personal Statement}
\end{center}
I am captivated by the interplay between theory and experiment in quantum information science, condensed matter, and atomic, molecular, and optical physics. In particular, I am interested in quantum simulations as well as experiments with ultracold gases for quantum science and fundamental physics. In May 2021, I will complete my undergraduate studies at Colby College with two Honors Theses on experimental atomic physics and mathematical analysis. My next objective is to expand and subsequently apply my research training to address an important open problem in quantum science. To that end, the Physics Ph.D. program at UIUC is a fantastic option.  \\ 


\input{content.tex}


At UIUC, I would like to focus my efforts on quantum science and expanding my teaching capacity. I have contacted Professor Bryan Clark and am interested in his theoretical research on computational condensed matter for quantum simulation and computation, which is closely related to my project with Dr. Hsieh at the Perimeter Institute. In particular, I find the mathematical aspects and numerical methods in Professor Clark's research very appealing. I am also attracted to Professor Brian DeMarco's work on quantum simulation with ultracold gases because it aligns directly with my experience in experimental atomic physics. Upon receiving my Ph.D., I aim to continue research in quantum science and eventually teach at a research-oriented university. Ultimately, I would like to make impactful contributions to the continually growing body of work in this field. I believe that admission to the Physics Ph.D. program at UIUC is an ideal step towards this goal. \\

\noindent Thank you for your consideration. \\

\noindent \today\\

	











	
	
	
	
	
\end{document}