\documentclass[12pt]{article}
\usepackage[left=1in, right=1in,top=1in,bottom=1in]{geometry}

%\usepackage{newpxtext,newpxmath}
\usepackage{amsfonts}
\usepackage{tgtermes}
\usepackage{color}
\usepackage{bold-extra}
\usepackage{setspace}
%\pagenumbering{gobble}
\setstretch{1.1}

\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{Huan Q. Bui}
\rhead{Application for MIT Physics}
%\cfoot{center of the footer!}
%\renewcommand{\headrulewidth}{0.4pt}
%\renewcommand{\footrulewidth}{0.4pt}

\begin{document}
\begin{center}
	\textbf{Personal Statement}
\end{center}
My parents' combined income as physicians in state-owned hospitals in Vietnam was hardly sufficient to cover my college tuition. However, I obtained financial aid from Colby with my strong high school academic performance. Since entering Colby, I have remained in the top 5\% of my class and am currently the highest ranking student, all of which come with additional financial aid. Moreover, I participate in work-study as a teaching assistant, which not only further offsets costs, but also allows me to help other students academically and learn about how their backgrounds shape their academic lives. Since I have thoroughly enjoyed this experience, the Ph.D. program is an ideal way for me to continue teaching, researching, and starting a career in academia. \\


As a Vietnamese international student amid recent events, many research opportunities outside of Colby are beyond my reach. However, I maximally utilized the resources available. I started research at Colby in my second semester, which led to my first summer project. Subsequently, I researched at Colby during the academic year and found non-REU projects elsewhere to broaden my experience. In 2019, I received an offer from the Joint Quantum Institute but my internship was cut short due to a major delay in OPT processing. In spite of this, I proactively learn about my project before starting, and thus the internship was successful. This summer, I received offers from the Institute for Quantum Computing and the Perimeter Institute to work on quantum information science. Both were then rescinded in March due to the pandemic, during which time not only did I begin research work for my Mathematics Honors Thesis to stay productive, but I also corresponded with my advisor at Perimeter. The Perimeter program eventually restarted in May in an online format, and with my preparation, it was also successful.\\

While there have been challenges, overcoming them and learning about the experiences of less privileged individuals have enriched my life. It is clear to me that I have been incredibly fortunate, and that even my biggest obstacles are merely mishaps for some. I can pursue my interest in physics because Colby has provided me with an inclusive and encouraging learning environment. At MIT and beyond, I wish to emulate such an environment through my work. \\

\noindent \today





















\end{document}