\documentclass{article}
\usepackage{physics}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{framed}
\usepackage{authblk}
\usepackage{empheq}
\usepackage{amsfonts}
\usepackage{esint}
\usepackage[makeroom]{cancel}
\usepackage{dsfont}
\usepackage{centernot}
\usepackage{mathtools}
\usepackage{bigints}
\usepackage{amsthm}
\theoremstyle{definition}
\newtheorem{defn}{Definition}[section]
\newtheorem{prop}{Proposition}[section]
\newtheorem{rmk}{Remark}[section]
\newtheorem{thm}{Theorem}[section]
\newtheorem{exmp}{Example}[section]
\newtheorem{prob}{Problem}[section]
\newtheorem{sln}{Solution}[section]
\newtheorem*{prob*}{Problem}
\newtheorem{exer}{Exercise}[section]
\newtheorem*{exer*}{Exercise}
\newtheorem*{sln*}{Solution}
\usepackage{empheq}
\usepackage{tensor}
\usepackage{xcolor}
%\definecolor{colby}{rgb}{0.0, 0.0, 0.5}
\definecolor{MIT}{RGB}{163, 31, 52}
\usepackage[pdftex]{hyperref}
%\hypersetup{colorlinks,urlcolor=colby}
\hypersetup{colorlinks,linkcolor={MIT},citecolor={MIT},urlcolor={MIT}}  
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}

\usepackage{newpxtext,newpxmath}
\newcommand*\widefbox[1]{\fbox{\hspace{2em}#1\hspace{2em}}}

\newcommand{\p}{\partial}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\lag}{\mathcal{L}}
\newcommand{\nn}{\nonumber}
\newcommand{\ham}{\mathcal{H}}
\newcommand{\M}{\mathcal{M}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\K}{\mathcal{K}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\w}{\omega}
\newcommand{\lam}{\lambda}
\newcommand{\al}{\alpha}
\newcommand{\be}{\beta}
\newcommand{\x}{\xi}
\def\dbar{{\mkern3mu\mathchar'26\mkern-12mu   d}}


\newcommand{\G}{\mathcal{G}}

\newcommand{\f}[2]{\frac{#1}{#2}}

\newcommand{\ift}{\infty}

\newcommand{\lp}{\left(}
\newcommand{\rp}{\right)}

\newcommand{\lb}{\left[}
\newcommand{\rb}{\right]}

\newcommand{\lc}{\left\{}
\newcommand{\rc}{\right\}}


\newcommand{\V}{\mathbf{V}}
\newcommand{\U}{\mathcal{U}}
\newcommand{\Id}{\mathcal{I}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\Z}{\mathcal{Z}}

%\setcounter{chapter}{-1}



\usepackage{enumitem}


\usepackage{subfig}
\usepackage{listings}
\captionsetup[lstlisting]{margin=0cm,format=hang,font=small,format=plain,labelfont={bf,up},textfont={it}}
\renewcommand*{\lstlistingname}{Code \textcolor{violet}{\textsl{Mathematica}}}
\definecolor{gris245}{RGB}{245,245,245}
\definecolor{olive}{RGB}{50,140,50}
\definecolor{brun}{RGB}{175,100,80}

%\hypersetup{colorlinks,urlcolor=colby}
\lstset{
	tabsize=4,
	frame=single,
	language=mathematica,
	basicstyle=\scriptsize\ttfamily,
	keywordstyle=\color{black},
	backgroundcolor=\color{gris245},
	commentstyle=\color{gray},
	showstringspaces=false,
	emph={
		r1,
		r2,
		epsilon,epsilon_,
		Newton,Newton_
	},emphstyle={\color{olive}},
	emph={[2]
		L,
		CouleurCourbe,
		PotentielEffectif,
		IdCourbe,
		Courbe
	},emphstyle={[2]\color{blue}},
	emph={[3]r,r_,n,n_},emphstyle={[3]\color{magenta}}
}






\begin{document}
		\begin{framed}
			\noindent Name: \textbf{Huan Q. Bui}\\
			Course: \textbf{8.333 - Statistical Mechanics I}\\
			Problem set: \textbf{\#6}
		\end{framed}
	
	
\noindent \textbf{1. Numerical Estimates.}

\begin{enumerate}[label=(\alph*)]
	\item For a typical metal, the ratio of the electron and phonon heat capacities at room temperature is 
	\begin{align*}
	blah
	\end{align*}
	
	\item 
	
	\item 
	
	\item \textbf{(Optional)}
\end{enumerate}


\noindent \textbf{2. Solar Interior.}

\begin{enumerate}[label=(\alph*)]
	\item 
	
	\item 
	
	\item 
	
	\item 
\end{enumerate}



\noindent \textbf{3. Density of States.}

\begin{enumerate}[label=(\alph*)]
	\item 
	
	\item 
	
	\item 
	
	\item 
	
	\item 
\end{enumerate}




\noindent \textbf{4. Quantum Point Particle Condensation.}

\begin{enumerate}[label=(\alph*)]
	\item 
	
	\item 
	
	\item 
	
	\item 
	
	\item 
\end{enumerate}




\noindent \textbf{5. Harmonic Confinement of Fermions.}


\begin{enumerate}[label=(\alph*)]
	\item 
	
	\item 
	
	\item 
	
	\item 
	
	\item 
	
	\item 
\end{enumerate}


\noindent \textbf{6. Anharmonic Trap.}

\begin{enumerate}[label=(\alph*)]
	\item 
	
	\item 
	
	\item 
	
	\item 
	
	\item 
	
	\item 
\end{enumerate}


\noindent \textbf{7. (Optional) Fermi gas in two dimensions.}

\begin{enumerate}[label=(\alph*)]
	\item 
	
	\item 
	
	\item 
	
\end{enumerate}


\noindent \textbf{8. (Optional) Partition of Integers.}

\begin{enumerate}[label=(\alph*)]
	\item 
	
	\item 
	
	\item 
	
\end{enumerate}


\noindent \textbf{9. (Optional) Fermions pairing into Bosons.}

\begin{enumerate}[label=(\alph*)]
	\item 
	
	\item 
	
	\item 
	
	\item 
	
\end{enumerate}


\noindent \textbf{10. (Optional) Ring Diagrams Mimicking Bosons.}

\begin{enumerate}[label=(\alph*)]
	\item 
	
	\item 
	
	\item 
	
	\item 

\end{enumerate}



\noindent \textbf{11. (Optional) Relativistic Bose Gas in $d$-dimensions.}

\begin{enumerate}[label=(\alph*)]
	\item 
	
	\item 
	
	\item 
	
	\item 
	
	\item 
\end{enumerate}



\noindent \textbf{12. (Optional) Surface Adsorption of an Ideal Bose Gas.}

\begin{enumerate}[label=(\alph*)]
	\item 
	
	\item 
	
	\item 
	
	\item 
	
\end{enumerate}



\noindent \textbf{13. (Optional) Inertia of Superfluid Helium.}

\begin{enumerate}[label=(\alph*)]
	\item 
	
	\item 
	
	\item 
	
	\item 
	
\end{enumerate}

	


\end{document}














