\documentclass[12pt]{article}
\usepackage[left=1in, right=1in,top=1.25in,bottom=1in]{geometry}

%\usepackage{newpxtext,newpxmath}
%\usepackage{amsfonts}
\usepackage{tgtermes}
\usepackage{color}
\usepackage{bold-extra}
\usepackage{setspace}
%\pagenumbering{gobble}
\usepackage{setspace}
\setstretch{1.1}
%\onehalfspacing

%\fontsize{12pt}{15pt}\selectfont

\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{Huan Q. Bui}
\rhead{Application for Harvard Physics}
%\cfoot{center of the footer!}
%\renewcommand{\headrulewidth}{0.4pt}
%\renewcommand{\footrulewidth}{0.4pt}

\begin{document}
\begin{center}
	\textbf{Statement of Purpose}
\end{center}
I am captivated by the interplay between theory and experiment in quantum information science, condensed matter, and atomic, molecular, and optical physics. In particular, I am interested in  quantum simulations as well as experiments with ultracold gases for quantum science and fundamental physics. In May 2021, I will complete my undergraduate studies at Colby College with two Honors Theses on experimental atomic physics and mathematical analysis. My next objective is to expand and subsequently apply my research training to address an important open problem in quantum science. To that end, the Physics Ph.D. program at Harvard University is a fantastic option.  \\ 

\input{content} 


At Harvard, I would like to focus my efforts on quantum science and expanding my teaching capacity. I have contacted Professor Mikhail Lukin, whose research on both theoretical and experimental aspects of quantum information science aligns directly with my experience and current interests. I am also interested in Professor Markus Greiner's research on quantum simulation with quantum gases and Professor John Doyle's work on the ACME precision measurement for the electron electric dipole moment. Upon receiving my Ph.D., I aim to continue research in these fields and eventually teach at a research-oriented university. Ultimately, I would like to make impactful contributions to the continually growing body of work in quantum science. I believe that admission to the Physics Ph.D. program at Harvard is an excellent first step towards this goal. \\


\noindent Thank you for your consideration. \\

\noindent \today
	











	
	
	
	
	
\end{document}